Assessing primitives performance\\ on multi-stage execution

### 2018-05-18 paper.tex
update linux results
update linux results - fix the 117 nonsense
update the asm comparison loop and figure 3 title
fix mistale

2   0.4222030   0.0008047936
3   1.028828    0.004597225
4   2.429007    0.002912642

@@

2   0.7673822   0.0011423885
3   1.843189    0.011583771
4   3.517044    0.019675605

@@

2   1.8905825   0.0119153480
3   4.041207   0.061090881
4   7.121638   0.010505603

@@

2   13.1217728   0.0170678541
3   17.708440   0.105891879
4   18.553670   0.023765562

@@

2   25.35945   0.1742098
3   25.42575   0.1621165
4   26.76261   0.186075

@@

   \end{subfigure}
   \subcaption*{\textbf{\LLVMMac}\vspace{-0.2cm}} %change vspace based on fig position
    \end{subfigure}
   \caption{String comparison benchmarks for strings of different sizes on different architectures.}
   \label{fig:bench}
\end{figure*}
\begin{table*}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
    & & 0 & 1 & 5 & 100 & 1000 \\
\hline
  \multirow{2}{*}{\legSlangPlug} &\GCCLinux& 0.422 $\pm$ 0.0008 & 0.767 $\pm$ 0.0011 & 1.891 $\pm$ 0.0119 & 13.12 $\pm$ 0.0171  & 25.36 $\pm$ 0.1742 \\
  						&\LLVMMac& 0.339 $\pm$ 0.0007 & 0.6238 $\pm$ 0.0012 & 1.5807 $\pm$ 0.0092 & 11.4096 $\pm$ 0.0474  & 23.21 $\pm$ 0.1789 \\
   \hline
  \multirow{2}{*}{\legSlang} &\GCCLinux& 1.029 $\pm$ 0.0046 & 1.843 $\pm$ 0.0116 & 4.041 $\pm$ 0.0611 & 17.71 $\pm$ 0.1059 & 25.43 $\pm$ 0.1621\\
 					 &\LLVMMac& 0.932 $\pm$ 0.0015 & 1.6900 $\pm$ 0.0030 & 3.241 $\pm$ 0.0067 & 10.149 $\pm$ 0.0321  & 12.939 $\pm$ 0.0177 \\
   \hline
  \multirow{2}{*}{\legRTL}  &\GCCLinux& 2.429 $\pm$ 0.0029 & 3.517 $\pm$ 0.0197  & 7.122 $\pm$ 0.0105 & 18.55 $\pm$ 0.0238 & 26.76 $\pm$ 0.1861\\
 				 	&\LLVMMac & 3.255 $\pm$ 0.0079 & 5.216 $\pm$ 0.0153 & 8.971 $\pm$ 0.0359 & 17.643 $\pm$ 0.06  & 24.881 $\pm$ 0.1983 \\
  \hline
\end{tabular} 
\vspace{0.2cm}
\caption{Benchmark results with standard errors. Average relative speed-up regarding baseline.}
\label{tab:detail_bench}
\end{table*}

\begin{figure*}[b!]
		\centering
		\includegraphics[width=1\linewidth]{figures/asm_cmp.pdf}
		\caption{\GCCLinux and \LLVMMac: different optimizations on the comparison loop.}
		\label{fig:Asm}
\end{figure*}

@@

\cba{Is next paragraph good ?}
We can draw the following patterns from these results:
\begin{itemize}
\item The \legSlangPlug implementation is slower than the baseline version for small strings (0,58 times slower for empty strings, 0,23 times slower for 1-character strings). This is due to the overhead of the calls to the main VM to access the object headers and the stack. On large strings, \legSlangPlug is one of the fastest implementation. 
\item The \legRTL implementation is more efficient than the baseline in every case. Nevertheless, the performance gap between this version and the \legSlangPlug and \legSlang ones tends to decrease as the string size increases, especially for \GCCLinux. For 1000-characters strings, the \legRTL version goes 0,25 times faster than the \legSlangPlug and the \legSlang versions.
\item The set-up used (either \GCCLinux or \LLVMMac) does lead to significant differences in terms of performance for the Slang implementation. 
\end{itemize}

We can explain these results based on the last 3 criteria detailed in Section~\ref{sec:implem_cmp}:

@@

\paragraph{Optimization potential on large strings comparison.}
The Plugin come with an overhead due the use of an interface. Besides, cross-file inlining is not performed for plugin, like said in Section~\ref{sec:implem_cmp}. These are some of the factors explaining the performance gap between these versions and the \legSlang and \legRTL ones.
When it comes to comparing large strings (100 characters and more), the execution time is mainly spent in the comparison loop (Figure~\ref{fig:Asm}). However, the switch overhead is still noticeable in the Slang implementation when strings of 100 characters are compared: Slang is 17.7 times faster than Baseline while Slang+JIT is 18,6 times faster than Baseline. 
This last observation only applies to the \GCCLinux results: the code generated by the LLVM compiler induces a longer execution time, as explained in the next paragraph.

>>>>

2   0.413386   0.0004942463
3   1.286553    0.004837948
4   3.343083    0.02105667

@@

2   0.745517   0.0008472452
3   2.256624    0.011554253
4   5.171014    0.02650453

@@

2   1.804201   0.0004602098
3   4.958408   0.011106844
4   8.714720   0.02207683

@@

2   12.047182   0.0088056909
3   17.240628   0.051498584
4   17.656653   0.04813202

@@

2   23.492410   0.0134896734
3   22.541872   0.077485955
4   24.927379   0.03087542

@@

   \end{subfigure}
   \subcaption*{\textbf{\LLVMMac}\vspace{-0.2cm}} %change vspace based on fig position
    \end{subfigure}
   \caption{String comparison benchmarks for strings of different sizes on different architectures. Average relative speed-up regarding baseline. Higher than 1 is better.}
   \label{fig:bench}
\end{figure*}
\begin{table*}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
    & & 0 & 1 & 5 & 100 & 1000 \\
\hline
  \multirow{2}{*}{\legSlangPlug} &\GCCLinux& 0.413 $\pm$ 0.0005 & 0.746 $\pm$ 0.0008 & 1.804 $\pm$ 0.0005 & 12.047 $\pm$ 0.0088 & 23.492 $\pm$ 0.0135 \\
  						&\LLVMMac& 0.339 $\pm$ 0.0007 & 0.6238 $\pm$ 0.0012 & 1.5807 $\pm$ 0.0092 & 11.4096 $\pm$ 0.0474  & 23.21 $\pm$ 0.1789 \\
   \hline
  \multirow{2}{*}{\legSlang} &\GCCLinux& 1.287 $\pm$ 0.0048 & 2.257 $\pm$ 0.0116 & 4.958 $\pm$ 0.0111 & 17.241 $\pm$ 0.0515 & 22.542 $\pm$ 0.0775\\
 					 &\LLVMMac& 0.932 $\pm$ 0.0015 & 1.6900 $\pm$ 0.0030 & 3.241 $\pm$ 0.0067 & 10.149 $\pm$ 0.0321  & 12.939 $\pm$ 0.0177 \\
   \hline
  \multirow{2}{*}{\legRTL}  &\GCCLinux& 3.343 $\pm$ 0.0211 & 5.171 $\pm$ 0.0265  & 8.715 $\pm$ 0.0221 & 17.657 $\pm$ 0.0481 & 24.927 $\pm$ 0.0309\\
 				 	&\LLVMMac & 3.255 $\pm$ 0.0079 & 5.216 $\pm$ 0.0153 & 8.971 $\pm$ 0.0359 & 17.643 $\pm$ 0.06  & 24.881 $\pm$ 0.1983 \\
  \hline
\end{tabular} 
\vspace{0.2cm}
\caption{Benchmark results with standard errors. Average relative speed-up regarding baseline.}
\label{tab:detail_bench}
\end{table*}

\begin{figure*}[b!]
		\centering
		\makebox[0pt]{
		\includegraphics[width=1.09\linewidth]{figures/asm_cmp.pdf}}
		\caption{\GCCLinux and \LLVMMac: different optimizations on the comparison loop.}
		\label{fig:Asm}
\end{figure*}

@@

%\cba{Is next paragraph good ?}
%We can draw the following patterns from these results:
%\begin{itemize}
%\item The \legSlangPlug implementation is slower than the baseline version for small strings (0,58 times slower for empty strings, 0,23 times slower for 1-character strings). This is due to the overhead of the calls to the main VM to access the object headers and the stack. On large strings, \legSlangPlug is one of the fastest implementation. 
%\item The \legRTL implementation is more efficient than the baseline in every case. Nevertheless, the performance gap between this version and the \legSlangPlug and \legSlang ones tends to decrease as the string size increases, especially for \GCCLinux. For 1000-characters strings, the \legRTL version goes 0,25 times faster than the \legSlangPlug and the \legSlang versions.
%\item The set-up used (either \GCCLinux or \LLVMMac) does lead to significant differences in terms of performance for the Slang implementation. 
%\end{itemize}

These results can be explained based on the last 3 criteria detailed in Section~\ref{sec:implem_cmp}:

@@

\paragraph{Optimization potential on large strings comparison.}
The Plugin comes with an overhead due the use of an interface. Besides, cross-file inlining is not performed for plugin, like said in Section~\ref{sec:implem_cmp}. These are some of the factors explaining the performance gap between these versions and the \legSlang and \legRTL ones.
When it comes to comparing large strings (100 characters and more), the execution time is mainly spent in the comparison loop (Figure~\ref{fig:Asm}). However, the switch overhead is still noticeable in the Slang implementation when strings of 100 characters are compared: Slang is 17.7 times faster than Baseline while Slang+JIT is 18,6 times faster than Baseline. 
This last observation only applies to the \GCCLinux results: the code generated by the LLVM compiler induces a longer execution time, as explained in the next paragraph.
